---
title: "Erosion Papers 2021"
format:
  html:
    toc: true
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r ref}
library(RefManageR)
bib <- ReadBib("./GIErosion2021.bib")
bib2 <- ReadBib("./conferences.bib", check = FALSE)
myopts <- BibOptions(
  bib.style = "authoryear",
  style = "html",
  first.inits = FALSE,
  no.print.fields = list("url", "urldate"),
  max.names = 20)

```

:::{.callout-note collapse="false"}

This webpage is an attempt to provide ASCE GI Geotechnics of Erosion committee members a reference list of ASCE papers on scour/erosion which are published between July 2020 to July 2021. It is for internal use only. 

:::


## Journal of Geotechnical and Geoenvironmental Engineering 

```{r, results = "asis"}
bib[journaltitle = "Journal of Geotechnical and Geoenvironmental Engineering"]
```


## International Journal of Geomechanics 

```{r, results = "asis"}
bib[journaltitle = "International Journal of Geomechanics"]
```

## More hydro/water related

Included journals are:

* Journal of Hydraulic Engineering
* Journal of Waterway, Port, Coastal, and Ocean Engineering 
* Journal of Hydrologic Engineering
* Journal of Irrigation and Drainage Engineering
* Journal of Water Resources Planning and Management
* Journal of Environmental Engineering





```{r, results = "asis"}
bib[journaltitle = list(
    "Journal of Hydraulic Engineering",
    "Journal of Waterway, Port, Coastal, and Ocean Engineering",
    "Journal of Hydrologic Engineering",
    "Journal of Irrigation and Drainage Engineering",
    "Journal of Water Resources Planning and Management",
    "Journal of Environmental Engineering")]
```

## More structural/material related

Included journals are:

* Journal of Engineering Mechanics
* Journal of Materials in Civil Engineering
* Journal of Bridge Engineering
* Journal of Performance of Constructed Facilities
* Natural Hazards Review

```{r, results = "asis"}
bib[journaltitle = list(
"Journal of Engineering Mechanics",
"Journal of Materials in Civil Engineering",
"Journal of Bridge Engineering",
"Journal of Performance of Constructed Facilities",
"Natural Hazards Review"
)]
```

## Other ASCE Conference proceedings

```{r, results = "asis"}
print(bib2, .opts = list(check.entries = FALSE))
```

