---
title: "ASCE Erosion Papers July 2020 -- June 2021"
format:
  html:
    toc: true
    toc-depth: 3
---

```{r, setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r ref}
library(RefManageR)
bib <- ReadBib("./GIErosion2021.bib")
bib2 <- ReadBib("./conferences.bib", check = FALSE)
myopts <- BibOptions(
  bib.style = "authoryear",
  style = "markdown",
  first.inits = FALSE,
  no.print.fields = list("url", "urldate"),
  max.names = 20)

```


:::{.callout-note collapse="false"}
This webpage is an attempt to provide ASCE GI Geotechnics of Erosion committee members a reference list of ASCE papers on scour/erosion which are published between July 2020 to June 2021. It is for internal use only. 
:::

## Introduction

The following list of papers was created based on the search results on [ASCE library](https://ascelibrary.org/). The "Advanced Search" mechanism was used and the publication date was limited to July 2020 to June 2021. The following keywords were used:

1. scour 
2. erosion
4. erodibility

The returned results are more than 1,000. I browsed the ranked lists based on relevance and selected around 60 papers which I feel are more of interests of our committee. The list is clearly incomplete and biased. So it is only intended to provide a reference for those who need it. 

Since it is based on searches, I believe some high quality papers were missing in the list. Therefore, **I invite you to send me the information of papers that deserve attention but not included in the list and I can then update it. **

To nominate a paper for the awards (including but not limited to Norman/Croes, and Middlebrooks), you can either email me via [jtao25 at asu.edu](), or submit your nomination **anonymously **using this [google form](https://forms.gle/Yb2ggyVsrCqmQgns9).

The list of papers are organised based on the journals/conferences they appear. Use the right-hand side panel to navigate. 

## List of publications

### Journal of Geotechnical and Geoenvironmental Engineering 

```{r, results = "asis"}
bib[journaltitle = "Journal of Geotechnical and Geoenvironmental Engineering"]
```

### International Journal of Geomechanics 

```{r, results = "asis"}
bib[journaltitle = "International Journal of Geomechanics"]
```

### More hydro/water related

Included journals are:

* Journal of Hydraulic Engineering
* Journal of Waterway, Port, Coastal, and Ocean Engineering 
* Journal of Hydrologic Engineering
* Journal of Irrigation and Drainage Engineering
* Journal of Water Resources Planning and Management
* Journal of Environmental Engineering


```{r, results = "asis"}
bib[journaltitle = list(
    "Journal of Hydraulic Engineering",
    "Journal of Waterway, Port, Coastal, and Ocean Engineering",
    "Journal of Hydrologic Engineering",
    "Journal of Irrigation and Drainage Engineering",
    "Journal of Water Resources Planning and Management",
    "Journal of Environmental Engineering")]
```

### More structural/material related

Included journals are:

* Journal of Engineering Mechanics
* Journal of Materials in Civil Engineering
* Journal of Bridge Engineering
* Journal of Performance of Constructed Facilities
* Natural Hazards Review

```{r, results = "asis"}
bib[journaltitle = list(
"Journal of Engineering Mechanics",
"Journal of Materials in Civil Engineering",
"Journal of Bridge Engineering",
"Journal of Performance of Constructed Facilities",
"Natural Hazards Review"
)]
```

### Other ASCE Conference proceedings

```{r, results = "asis"}
print(bib2, .opts = list(check.entries = FALSE))
```

